Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-11-21 KuengR__Lens_models.tex
cleanup: backport arxiv modifications
cleanup: enter acceptance date

@@

% I disabled hyperlink in the cls und included it here because of bugs
\usepackage{hyperref}   % Hyperlinks
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}

@@

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

>>>>

\pdfoutput=1
% pdfoutput is used for arxiv, should be somewhere in lines 1-5

@@

% I disabled hyperlink in the cls und included it here because of bugs
\usepackage{hyperref}   % Hyperlinks
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  filecolor=blue,
  urlcolor=blue,
  pdfauthor={Kueng, Rafael et al.},
  pdftitle={Models of gravitational lens candidates from Space Warps CFHTLS}
}

@@

% These dates will be filled out by the publisher
\date{Accepted 2017 November 19 . Received 2017 November 19 ; in original form 2017 May 02}
